---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SurrConformalDR

<!-- badges: start -->
<!-- badges: end -->

An R package for Surrogate-assisted Conformal Inference for Efficient Individual Causal Effect Estimation

## Installation

To implement the method and access the vignette, you can install the development version of SurrConformalDR from [GitHub](https://github.com/) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("Gaochenyin/SurrConformalDR",
                         build_vignettes = TRUE)
browseVignettes('SurrConformalDR')
```

## Example 1: Surrogate-assisted efficient conformal inferece

We illustrate the use of the SurrConformalDR package by generating a synthetic dataset with continuous primary outcomes. For additional details, please consult the respective vignette by running: `vignette("demo_SCIENCE", package = "SurrConformalDR")`

```{r include=FALSE}
library(SurrConformalDR)
library(dplyr)
library(SuperLearner)
```

```{r example, echo=TRUE, warning=FALSE}
# Sample size
N <- 1e4

# SuperLearner library
SL.library <- c("SL.glm")

# Set random seed
seed <- 2333

# Generate a synthetic dataset with continuous outcomes
df <- genData.conformal(
  seed = seed, 
  N = N, 
  outcome.type = "Continuous",
  beta.S = 10
)

head(df)
```




```{r conformalInference, echo=TRUE, warning=FALSE}
set.seed(1234)

# Create two folds (75% training, 25% evaluation)
train.idx <- caret::createDataPartition(seq_len(nrow(df)), p = 0.75)$Resample1
eval.idx <- setdiff(seq_len(nrow(df)), train.idx)

# Apply the Surrogate-Assisted Conformal Inference (SCIENCE) framework
df_rst_wS <- SurrConformalDR(
  df, 
  train.idx = train.idx, 
  eval.idx = eval.idx,
  SL.library = SL.library,
  outcome.type = "Continuous",
  alphaCI = 0.05, 
  nested = TRUE
)

# Compute empirical coverage for the observed outcomes when D = 1
coverage_D1 <- mapply(
  function(y, lower, upper) lower <= y & upper >= y, 
  y     = (df_rst_wS %>% filter(D == 1))$Y,
  lower = (df_rst_wS %>% filter(D == 1))$lower.Y,
  upper = (df_rst_wS %>% filter(D == 1))$upper.Y
) %>% mean(na.rm = TRUE)

coverage_D1
```



## Example 2: Surrogate-assisted clustered conformal inferece for fairness

We now demonstrate the package's clustered conformal inference features, which aim to enhance fairness across different protected groups.
```{r}
# Generate a synthetic dataset with categorical outcomes
df <- genData.clustered.conformal(
  seed = seed,
  N = N,
  numgroup = 3, 
  numcluster = 2,
  outcome.type = "Categorical",
  beta.S = 10
)

head(df)
```

```{r ClusteredconformalInference, echo=TRUE, warning=FALSE}
set.seed(1234)

# Create two folds (75% training, 25% evaluation)
train.idx <- caret::createDataPartition(seq_len(nrow(df)), p = 0.75)$Resample1
eval.idx <- setdiff(seq_len(nrow(df)), train.idx)

# SCIENCE framework: efficient conformal inference
rst.wS <- SurrConformalDR(
  df,
  train.idx = train.idx, 
  eval.idx = eval.idx,
  SL.library = SL.library,
  outcome.type = "Categorical",
  alphaCI = 0.05, 
  nested = TRUE
)

# SAGCCI framework: surrogate-assisted clustered conformal inference
rst.wSCluster <- SurrClusterConformalDR(
  df,
  train.idx,
  eval.idx,
  numcluster = "auto",
  minsize = 1 / 0.05 - 1,
  outcome.type = "Categorical",
  SL.library = SL.library,
  alphaCI = 0.05
)

# Evaluate metrics:
# 1) CovGap (coverage gap for fairness)
# 2) AvgSize (average size for efficiency)
get.metric(rst.wS)
get.metric(rst.wSCluster)

# The SAGCCI approach often reduces coverage gap (CovGap) 
# while maintaining a similar average prediction interval size (AvgSize).
```












