---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SurrConformalDR

<!-- badges: start -->
<!-- badges: end -->

An R package for Surrogate-assisted Conformal Inference for Efficient Individual Causal Effect Estimation

## Installation

To access the vignette, you can install the development version of SurrConformalDR from [GitHub](https://github.com/) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("Gaochenyin/SurrConformalDR",
                         build_vignettes = TRUE)
browseVignettes('SurrConformalDR')
```

## Example

We illustrate the usage of `SurrConformalDR` using simple synthetic datasets for continuous primary outcomes. For details please read the vignette (`vignette("demo_SCIENCE", package = "SurrConformalDR")`)
```{r include=FALSE}
library(SurrConformalDR)
library(dplyr)
library(SuperLearner)
```

```{r example, echo=TRUE, warning=FALSE}
## basic example code
# sample size
N <- 1e4
# library for SuperLearner
SL.library <- c('SL.glm')
seed <- 2333
# an example for Gaussian outcomes
df <- genData.conformal(seed = seed, N = N, 
                        outcome.type = 'Continuous',
                        beta.S = 10)
head(df)
```

```{r conformalInference, echo=TRUE, warning=FALSE}
set.seed(1234)
# create two folds (75% for training and 25% for evaluation)
train.idx <- caret::createDataPartition(1:nrow(df), p = 0.75)$Resample1
eval.idx <- setdiff(1:nrow(df), train.idx)
# SCIENCE framework
df_rst_wS <- SurrConformalDR(df, 
                        train.idx = train.idx, 
                        eval.idx = eval.idx,
                        SL.library = SL.library,
                        outcome.type = 'Continuous',
                        alphaCI = 0.05, nested = TRUE)
## empirical coverage of the observed outcomes for D = 0 and 1
## D = 1: source data, the primary outcomes are observed
mapply(function(y, lower, upper)lower <= y & upper >= y, 
       y = (df_rst_wS%>%filter(D==1))$Y, 
       lower = (df_rst_wS%>%filter(D==1))$lower.Y,
       upper = (df_rst_wS%>%filter(D==1))$upper.Y) %>% 
   mean(na.rm = TRUE)

